### 2012-01-28 docs/SDC/sdc.tex
minor fixes

In the Strang-split version of \maestro, the reaction network solves just
the reaction portion of the species evolution equations along with a
temperature evolution equation.  This is done using a standard ODE solver
(like {\tt VODE}) on the system:
\begin{eqnarray}
\frac{dX_k}{dt} &=& \omegadot_k(\rho,X_k,T) \\
\frac{dT}{dt}   &=& 
    \frac{1}{c_p} \left ( -\sum_k \xi_k  \omegadot_k  + \Hnuc \right ).
\end{eqnarray}
Here, $T$ is evolved solely to evaluate the reaction rates,
$\omegadot_k(\rho,X_k,T)$.  Furthermore, we simplify the problem
``freezing'' the thermodynamics---i.e., $c_p$ is evaluating at the
start of the integration and held constant thereafter.

@@

\section{Summary of Changes}
The major changes from the non-SDC-enabled burners is the addition of
the advective terms to the system of ODEs, the fact that we integrate
$(\rho X_k)$ instead of just $X_k$, and the need to derive the
temperature from the input state for each RHS evaluation by {\tt
  VODE}.

>>>>

In the Strang-split version of \maestro, the reaction network solves just
the reaction portion of the species evolution equations along with a
temperature evolution equation.  This is done using a standard ODE solver
(like {\tt VODE}) on the system:
\begin{eqnarray}
\frac{dX_k}{dt} &=& \omegadot_k(\rho,X_k,T) \\
\frac{dT}{dt}   &=& 
    \frac{1}{c_p} \left ( -\sum_k \xi_k  \omegadot_k  + \Hnuc \right ).
\end{eqnarray}
Here, $T$ is evolved solely to evaluate the reaction rates,
$\omegadot_k(\rho,X_k,T)$.  Furthermore, we simplify the problem
``freezing'' the thermodynamics---i.e., $c_p$ and $\xi_k$ are evaluated at the
start of the integration and held constant thereafter.

@@

\section{Summary of Changes}
The major changes from the non-SDC-enabled burners is the addition of
the advective terms to the system of ODEs, the fact that we integrate
$(\rho X_k)$ instead of just $X_k$, integrate $(\rho h)$ instead
of $T$, and the need to derive the
temperature from the input state for each RHS evaluation by {\tt
  VODE}.
